Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-11-15 analysis/paper/sim_survey_paper.Rmd
Add plot_grid function

The `make_grid` function is used to generate the grid used in the case study, and the `sim_distribution` function distributes the population, `n`, simulated above using `sim_abundance` through the grid:

>>>>

The `make_grid` function is used to generate a survey grid for use in the `sim_distribution` function. The output from `make_grid` is a raster object [@hijmans2016] with four layers: `depth`, `cell`, `division` and `strat`. If a more detailed and realistic grid is required, users can manually generate their own survey grid using real data and this grid can be supplied to `sim_distribution` if the same structure is used. The settings used to make the grid used in our case study are shown in Table \@ref(tab:par) and these settings are also the defaults. Below we generate and plot (combined in Figure \@ref(fig:grid)) a default grid and another grid with a more linear gradient in depth.

```{r, echo = TRUE, eval = FALSE}
a <- make_grid()
b <- make_grid(shelf_depth = 500, shelf_width = 0, depth_range = c(0, 1000))
plot_grid(a)
plot_grid(b)
```

```{r grid, fig.cap = "- Plots produced by `plot_grid` when supplied an raster object produced by a) `make_grid()` and b) `make_grid(shelf_depth = 500, shelf_width = 0, depth_range = c(0, 1000))`."}

a <- make_grid() %>% 
  plot_grid(showscale = FALSE) %>% 
  add_annotations(x = 0, y = 1, xref = "paper", yref = "paper", showarrow = FALSE,
                  text = "a)")
b <- make_grid(shelf_depth = 500, shelf_width = 0, depth_range = c(0, 1000)) %>% 
  plot_grid(showscale = FALSE) %>% 
  add_annotations(x = 0.01, y = 1, xref = "paper", yref = "paper", showarrow = FALSE,
                  text = "b)")
p <- subplot(a, b)

export_plot(p, file = "analysis/paper/figures/plot_grid.png", width = 800, height = 460)
knitr::include_graphics("figures/plot_grid.png")

```

With a population simulated

, and the `sim_distribution` function distributes the population simulated above using `sim_abundance` through the grid:
